The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems

### 2012-05-01 shortRange.inhomo/alltext/pubilsh/main.tex
small revises

\section{Conclusions}\label{sec:conclusion}

@@

{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate can be more general than the studied examples.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald family algorithms, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}

>>>>

\section{Conclusions and discussions}\label{sec:conclusion}

@@

{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate is more general than the studied examples,
  because we only assumed the interaction is short-ranged and
  treated by the cut-off method.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald family algorithms, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  However, it is impossible to test all possible cases within one paper.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}
